P.berghei pir analysis

### 2021-03-12 Manuscript_pirAnalysis_Github/Pberghei/Manuscript_Github_Pberghei_pir.Rmd
Some better descriptions

```{r setup, include=FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, results = TRUE, message = FALSE, warning = FALSE)
# Set below to your own working directory.
knitr::opts_knit$set(root.dir = 
                       ".")
options(scipen = 999) # Means that numbers are displayed normally not as 1e6 (1000000)
# getwd()

@@

```{r function_mround}
mround <- function(x,base){ 
  base*ceiling(x/base) 
} 
```

```{r function_my_max}
my_max <- function(x) ifelse( !all(is.na(x)), max(x, na.rm=T), NA) #max robust to NAs
```

```{r function_uniquify}
uniquify <- function(vector_names, first_one = TRUE){
  new_vector <- c()
  df_num <- data.frame(names = unique(vector_names), rep = 1)
  if(first_one){
    duplicated_names <- unique(vector_names[duplicated(vector_names)])
  }else{
    duplicated_names <- c()
  }
  for(i in 1:length(vector_names)){
    if(vector_names[i] %in% duplicated_names|!first_one){
    name <- paste(vector_names[i],
                  df_num$rep[match(vector_names[i], df_num$names)],
                  sep = '_')
    #Increase rep counter
    df_num$rep[match(vector_names[i], df_num$names)] <- df_num$rep[match(vector_names[i], df_num$names)] + 1
    new_vector[i] <- name
    }else{
      new_vector[i] <- vector_names[i]
    }
  }
  new_vector
}
```

@@

```{r function_ordering}
ordering = function(to_order, order_vector){
  order = unlist(sapply(order_vector, 
                        function(x){unique(str_subset(to_order, 
                                                      pattern = paste(x)))}))
  order_missing = unique(to_order[!to_order %in% order])
  unique(c(order, order_missing), fromLast = TRUE)
}

@@

# We need to write a function to calculate the TPM from the count data we have generated. This function uses the _lengths.transcript_ object created in the chunk above and should generate errors if it detects discrepencies between the Geneids so that the wrong transcript length is not used.

@@

```{r pir/fam_id, message=FALSE, results='hide'}

# Getting the pir/fam gene names and transcript lengths needed for calculating the transcript-per-million

@@

#Remove the Caldelari 6h samples, as they did in their paper.

>>>>

```{r setup, include=FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, results = TRUE, message = FALSE, warning = FALSE)
# Set below to your own working directory.
knitr::opts_knit$set(root.dir = 
                       ".")
options(scipen = 999) # Means that numbers are displayed normally not as 1e6 (1000000)
```

@@

```{r function_mround}
#Make nicer numbers rounded up, useful for making scales for a plot.
mround <- function(x,base){ 
  base*ceiling(x/base) 
} 
```

```{r function_my_max}
#max robust to NAs
my_max <- function(x) ifelse( !all(is.na(x)), max(x, na.rm=T), NA) 
```

```{r function_uniquify}
#Make unique identifiers from a vector of names by appending '_X' where X is the number of the 'replicate'.
uniquify <- function(vector_names, first_one = TRUE){
  new_vector <- c()
  df_num <- data.frame(names = unique(vector_names), rep = 1)
  if(first_one){
    duplicated_names <- unique(vector_names[duplicated(vector_names)])
  }else{
    duplicated_names <- c()
  }
  for(i in 1:length(vector_names)){
    if(vector_names[i] %in% duplicated_names|!first_one){
    name <- paste(vector_names[i],
                  df_num$rep[match(vector_names[i], df_num$names)],
                  sep = '_')
    #Increase rep counter
    df_num$rep[match(vector_names[i], df_num$names)] <- df_num$rep[match(vector_names[i], df_num$names)] + 1
    new_vector[i] <- name
    }else{
      new_vector[i] <- vector_names[i]
    }
  }
  new_vector
}
```

@@

```{r function_ordering}
#Use an order_vector of partial string matches to order.
ordering = function(to_order, order_vector){
  order = unlist(sapply(order_vector, 
                        function(x){unique(str_subset(to_order, 
                                                      pattern = paste(x)))}))
  order_missing = unique(to_order[!to_order %in% order])
  unique(c(order, order_missing), fromLast = TRUE)
}

@@

# We need to write a function to calculate the TPM from the count data we have generated. This function uses the _lengths.transcript_ object and should generate errors if it detects discrepancies between the Geneids so that the wrong transcript length is not used.

@@

```{r pir_id, message=FALSE, results='hide'}

# Getting the pir gene names and transcript lengths needed for calculating the transcript-per-million

@@

#Remove the Caldelari (E06) 6h samples, as they did in their paper.
